troubleshooting

### 2024-09-30 README.Rmd
4 spaces for indents
Bioccheck changes

```{r}
colData <- readr::read_csv(system.file("extdata/colData.csv", package = "mspms"))

@@

```{r}
combined_peptide_filepath <- system.file("extdata/fragpipe_combined_peptide.tsv",
  package = "mspms"
)

>>>>

```{r}
colData <- readr::read_csv(system.file("extdata/colData.csv",
    package = "mspms"
))

@@

```{r}
combined_peptide_filepath <- system.file("extdata/fragpipe_combined_peptide.tsv",
                                        package = "mspms")
